Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-25 robdml.tex
tex

\oo{[3. Intra-Class Structure]}
Given a triplet of samples, we may eventually get up to 6 samples avaiable
for adversarial training. There could be some kind of hierarchy.

% evaluation and conclusion
We conduct experiments
on three commonly used DML dataset, namely CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford
Online Product~\cite{sop}.
%
The proposed method overwhelmingly outperforms the state-of-the-art defense
in terms of robustness, training cost, as well as the penalty on benign
example retrieval.
%
Our conclusions are:
%
(1) Triplet sampling strategy is vital for adversarial training of tripet-loss
based DML models.
%
\oo{...}

% contributions
In brief, our contribusions include:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) is proposed as a flexible tool
		to create adversarial triplets with increased hardness for
		subsequent adversarial training.
		%
		It is more efficient than previous adversarial training methods of DML.
		%
	\item \textit{Gradual Adversary} is proposed as a family of pseudo-hardness
		functions for \emph{Hardness Manipulation}, which can balance the
		training objectives during the training process.
		%
		A linear function named Simple Graduate Adversary (SGA) is designed as
		an example.
		%
	\item \oo{TODO} Inter-ID structure constraint. ((aa~p) + (pp~a))/2
		(cross-id repelling) existing methods only care inter-class separation,
		but not intra-class (inter-id) separation, because we may get a
		6-element set (a,a~,p,p~,n,n~) from the original triplet.
		%
\end{enumerate}

>>>>

% evaluation and conclusion
The experiments are conducted on three commonly used DML datasets, namely
CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196}, and Stanford Online
Product~\cite{sop}.
%
The proposed method overwhelmingly outperforms the state-of-the-art defense in
terms of training cost, robustness, as well as the performance on benign
example retrieval.

% contributions
In brief, our contribusions includes:
%
\begin{enumerate}[nosep, noitemsep, leftmargin=*]
	%
	\item {\textit{Hardness Manipulation}} (HM) is proposed as a flexible tool
		to create adversarial triplets with increased hardness for
		subsequent adversarial training.
		%
		It is more efficient than previous adversarial training methods of DML.
		%
	\item \textit{Gradual Adversary} is proposed as a family of pseudo-hardness
		functions for \emph{Hardness Manipulation}, which can balance the
		training objectives during the training process.
		%
		A linear function named Simple Graduate Adversary (SGA) is designed as
		an example.
		%
	\item \textit{Intra-Class Structure} penalty is proposed to further improve
		the robustness of a DML model, while such possibility is neglected by
		existing methods. 
		%
\end{enumerate}
